---
title: "Survey of PATO - the Phenotype And Trait Ontology"
author: "Nicolas Matentzoglu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    html_document: default 
editor_options: 
  chunk_output_type: console
---


```{r, echo=FALSE}
library(data.table)
library(stringr)
library(plyr)
library(ggplot2)
library(DT)
library(knitr)
```


```{r settings, echo=FALSE}
ws = "pato_survey_obo.RData"

fontsize=2

rbox_types<-c("SubPropertyChainOf", "SubObjectPropertyOf", "ObjectPropertyDomain","EquivalentObjectProperties","ObjectPropertyRange", "InverseObjectProperties", "TransitiveObjectProperty", "ReflexiveObjectProperty", "AsymmetricObjectProperty", "IrrefexiveObjectProperty", "InverseFunctionalObjectProperty", "FunctionalObjectProperty", "SymmetricObjectProperty", "DisjointObjectProperties","DisjointDataProperties","SubDataPropertyOf","EquivalentDataProperties","ObjectPropertyDomain","DataPropertyDomain","ObjectPropertyRange","DataPropertyRange","FunctionalDataProperty","DatatypeDefinition","HasKey")

rule_types<-c("Rule")

abox_types<-c("ClassAssertion", "ObjectPropertyAssertion","SameIndividual","DifferentIndividuals","NegativeObjectPropertyAssertion","DataPropertyAssertion","NegativeDataPropertyAssertion")

tbox_types<-c("SubClassOf", "EquivalentClasses","DisjointClasses","DisjointUnion")

characteristics_axiom_types<-c("TransitiveObjectProperty", "ReflexiveObjectProperty", "AsymmetricObjectProperty", "IrrefexiveObjectProperty", "InverseFunctionalObjectProperty", "FunctionalObjectProperty", "SymmetricObjectProperty")

options(scipen = 1000)
opts_chunk$set(fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE)
```

```{r functions, echo=FALSE}
pc<-function(x,y,digits=2) {
  return(round(100*(x/y),digits))
}

theme_survey<-function(p) {
  cls<-c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
  p + theme_bw()+theme(axis.text.x = element_text(size=12),axis.text.y = element_text(size=12),axis.title = element_text(size=12)) + scale_fill_brewer(palette = "Paired") + scale_colour_brewer(palette = "Paired")
 # +  scale_color_manual(values=cls) +   scale_fill_manual(values=cls)
}

kt<-function(x) {
  return(kable(x,row.names = FALSE,digits = c(2)))
}
```

```{r load, echo=FALSE, cache=TRUE}
load(ws)
o_labels<-unique(df_p[,c("iri","label")])
```

```{r pre_obocorpus, echo=FALSE}
d_obo<-ct_download_sucess[,]
#df_corpus$merged_success<-TRUE
#hwarning("REMOVE THIS")
all<-(df_corpus$o)
notdownloaded<-(df_corpus[!df_corpus$download_success,]$o)
downloadnotmerged<-(df_corpus[df_corpus$download_success&!df_corpus$merged_success,]$o)
mergednotcollected<-(df_corpus[df_corpus$merged_success&!df_corpus$collectdata_success,]$o)
collectedbutexcluded<-(df_corpus[df_corpus$collectdata_success&df_corpus$excluded,]$o)
ct_ont_all<-length(all)
ct_ont_download_fail<-length(notdownloaded)
ct_ont_merge_fail<-length(downloadnotmerged)
ct_ont_collect_fail<-length(mergednotcollected)
ct_ont_excluded<-length(collectedbutexcluded)

st_ont_all<-paste(all,collapse=" ")
st_ont_download_fail<-paste(notdownloaded,collapse=" ")
st_ont_merge_fail<-paste(downloadnotmerged,collapse=" ")
st_ont_collect_fail<-paste(mergednotcollected,collapse=" ")
st_ont_excluded<-paste(collectedbutexcluded,collapse=" ")

ct_corp_obo<-ct_ont_all-ct_ont_download_fail-ct_ont_merge_fail-ct_ont_collect_fail-ct_ont_excluded
```

# The OBO Corpus
In the following we will describe the OBO corpus in general. The OBO corpus contains `r ct_ont_all` ontologies, 

* `r ct_ont_download_fail` of which failed to download: `r st_ont_download_fail`, 
* `r ct_ont_merge_fail` of which failed to be parsed by ROBOT (or were empty): `r st_ont_merge_fail`
* `r ct_ont_collect_fail` of which failed to be processed by the data collection pipeline (timeout 60min): `r st_ont_collect_fail`
* `r ct_ont_excluded` of which failed were manually excluded: `r st_ont_excluded` 

resulting in a total of `r ct_corp_obo` valid ontologies for the following analysis. Full breakdown:

```{r processingbd, echo=FALSE}
kt(d_obo)
```
  
```{r prepro_obo, echo=FALSE}
# Analysis of OBO snapshot
# IN df_ax, df_p
df_ax$ax_cat<-ifelse((df_ax$axiomtype %in% tbox_types),"tbox",ifelse((df_ax$axiomtype %in% abox_types),"abox",ifelse((df_ax$axiomtype %in% rule_types),"rules",ifelse((df_ax$axiomtype %in% rbox_types),"rbox","other"))))
# If a Tbox axiom contains only PATO classes we assume it is a PATO axiom that got merged in and drop it.
df_ax$pato_axiom<-ifelse(df_ax$pato_only&df_ax$ax_cat=="tbox",TRUE,FALSE)
df_ax<-df_ax[!df_ax$pato_axiom,]
df_ax$corpussize <- ct_corp_obo
df_p$corpussize <- ct_corp_obo

# PATO axiom data (raw)
da<-df_ax
da$all="all"
dm<-df_ax[df_ax$ftype=="merged",]
dni<-df_ax[df_ax$ftype=="noimports",]

dsig_m<-df_p[df_p$ftype=="merged",c("iri","o")]
dsig_ni<-df_p[df_p$ftype=="noimports",c("iri","o")]

ct_allaxiomdata$ax_cat<-ifelse((ct_allaxiomdata$axiomtype %in% tbox_types),"tbox",ifelse((ct_allaxiomdata$axiomtype %in% abox_types),"abox",ifelse((ct_allaxiomdata$axiomtype %in% rule_types),"rules",ifelse((ct_allaxiomdata$axiomtype %in% rbox_types),"rbox","other_cat"))))

# All axiom data (counted)
daa<-ct_allaxiomdata
daa$all="all"

ct_unique_o_using_rel<-length(unique(dm$o))
ct_unique_o_using_rel_ni<-length(unique(dni$o))
# OUT dm, dni, dm, dni, corpus, dsig_m, dsig_ni, ct_unique_o_using_rel, ct_unique_o_using_rel_ni, 
```

# How important is the PATO for OBO foundry ontologies? 
We say that an axiom ax is *PATO-dependent* if the axiom contains one or more PATO-classes. An ontology is PATO-dependent if it contains at least one PATO-dependent axiom. We say that an axiom is *p-dependent* if it contains a particular PATO class p. In the following, we will quantify the importance of PATO for OBO ontologies by (1) counting the number of PATO-dependent ontologies and (2) determining the prevalence of PATO-dependent axioms. If a TBox axiom ("SubClassOf", "EquivalentClasses","DisjointClasses","DisjointUnion") contains a set of classes [C1,C2..,Cn], all of which are PATO classes (i.e. having a PATO iri), we *make the assumption that this is a PATO axiom*. Those PATO axioms are *removed from the axiom analysis* (but not from the ontology level analysis; if the PATO class is mentioned, it is counted as mentioned). This mitigates overcounting PATO-dependent axioms that are imported from PATO and then phyiscally merged into the release artefact (which happens relatively often). 

```{r breakdown_o, echo=FALSE, include=FALSE}
# OBO ontologies and PATO class usage. Ignored now in favour of axiom-based counting
#IN: dsig_m, dsig_ni
dsig_m_unique<-unique(dsig_m[,c("iri","o")])
dsig_ni_unique<-unique(dsig_ni[,c("iri","o")])
dsig_m_o_ct<-count(dsig_m_unique[,c("o")])
names(dsig_m_o_ct)<-c("o","ct_sig_m")
dsig_ni_o_ct<-count(dsig_ni_unique[,c("o")])
names(dsig_ni_o_ct)<-c("o","ct_sig_ni")
df_o<-merge(dsig_ni_o_ct,dsig_m_o_ct,by="o",all=TRUE)
df_o[is.na(df_o)] <- 0
#write.csv(file = "pato_survey_onts.csv",df_o)
names(df_o)<-c("Ontology","PATO classes (no imports)","PATO classes (merged imports)")
kt(df_o)
dsig_m_unique<-dsig_ni_unique<-dsig_m_o_ct<-dsig_ni_o_ct<-NULL
# OUT: df_o
```

## Analysis of PATO-dependent ontologies

```{r rodeo, echo=FALSE}
df_rodeo<-unique(da[,.(o,ax_cat,ftype)])
ct_rodeo_axcat<-count(df_rodeo[,.(ax_cat,ftype)])
names(ct_rodeo_axcat)<-c("category","ftype","freq")

df_rodeo3<-unique(da[,.(o,all,ftype)])
ct_rodeo_all<-count(df_rodeo3[,.(all,ftype)])
names(ct_rodeo_all)<-c("category","ftype","freq")

x<-merge(ct_rodeo_axcat,ct_rodeo_all,by=c("category","ftype","freq"),all=TRUE)
x$pc<-pc(x$freq,ct_corp_obo,1)
d_rodeo<-x
```

```{r rodeo_p, echo=FALSE}
p<-ggplot(d_rodeo,aes(x=reorder(category,freq),y=pc,fill=ftype,group=ftype)) + geom_bar(stat="identity",position="dodge") + geom_text(aes(label=paste("",freq," (",pc,"%)",sep="")), hjust=-0.1,vjust=0.5, color="black",position = position_dodge(width = 1),size=3.5) + scale_x_discrete(limits = c("abox","rules","tbox","rbox","all")) + xlab("") + ylab("% of OBO ontologies") + guides(fill=guide_legend(title="Imports")) + coord_flip()
theme_survey(p) + theme(legend.position = c(0.8, 0.2)) + ylim(0,100)
ggsave("patosurvey_rodeo.jpg",width = 4.5,height = 3.5)
```

## Analysis of PATO-dependent axioms

```{r aggregate_all_axioms, echo=FALSE}

ct_allaxiomdata_axcat<-aggregate(daa$freq,by=list(daa$ftype,daa$corpus,daa$ax_cat),FUN=sum)
names(ct_allaxiomdata_axcat)<-c("ftype","corpus","category","freq")

ct_allaxiomdata_all<-aggregate(daa$freq,by=list(daa$ftype,daa$corpus,daa$all),FUN=sum)
names(ct_allaxiomdata_all)<-c("ftype","corpus","category","freq")


x<-merge(ct_allaxiomdata_all,ct_allaxiomdata_axcat,by=c("category","ftype","freq","corpus"),all=TRUE)
x$corpus<-NULL
names(x)<-c("category","ftype","ax_ct")
d_roallax<-x
```

```{r aggregate_ro_axioms, echo=FALSE}
df_rodeo<-unique(da[,.(o,ax_cat,axiomid,ftype)])
ct_rodeo_axcat<-count(df_rodeo[,.(ax_cat,ftype)])
names(ct_rodeo_axcat)<-c("category","ftype","freq")

df_rodeo3<-unique(da[,.(o,all,axiomid,ftype)])
ct_rodeo_all<-count(df_rodeo3[,.(all,ftype)])
names(ct_rodeo_all)<-c("category","ftype","freq") 

x<-merge(ct_rodeo_axcat,ct_rodeo_all,by=c("category","ftype","freq"),all=TRUE)

x<-merge(x,d_roallax,by=c("category","ftype"))
x$pc<-pc(x$freq,x$ax_ct,1)
d_roax<-x

```

```{r roaxplot, echo=FALSE}
p<-ggplot(d_roax,aes(x=reorder(category,freq),y=pc,fill=ftype,group=ftype)) + geom_bar(stat="identity",position="dodge") + geom_text(aes(label=paste("",freq,sep="")), hjust=-0.1,vjust=0.5, color="black",position = position_dodge(width = 1),size=3.5) + scale_x_discrete(limits = c("abox","rules","tbox","rbox","all")) + xlab("") + ylab("% of axioms across OBO-foundry") + guides(fill=guide_legend(title="Imports")) + coord_flip()
theme_survey(p) + theme(legend.position = c(0.85, 0.8)) + ylim(0,35)
ggsave("rosurvey_axiomcat.jpg",width = 4.5,height = 3.5)
```

# How important are the individual PATO classes?

```{r prep_plots, echo=FALSE}
#IN: dm, dni
dm$corpussize<-ct_corp_obo
dni$corpussize<-ct_corp_obo
dgg<-unique(dm[,c("iri","label","o","corpussize")])
cdgg<-count(dgg[,c("iri","label","corpussize")])
cdgg$pc<-round(pc(cdgg$freq,cdgg$corpussize),0)
cdgg$type<-"merged"
cdgg$corpussize<-NULL

dgg_ni<-unique(dni[,c("iri","label","o","corpussize")])
cdgg_ni<-count(dgg_ni[,c("iri","label","corpussize")])
cdgg_ni$pc<-round(pc(cdgg_ni$freq,cdgg_ni$corpussize),0)
if(nrow(cdgg_ni)>=1) {
  cdgg_ni$type<-"removed"
}
cdgg_ni$corpussize<-NULL

x<-rbind(cdgg,cdgg_ni)
dgg<-dgg_ni<-cdgg_ni<-cdgg<-NULL

x<-reshape(x, idvar = c("iri","label"), timevar = "type", direction = "wide")
x$top20<-ifelse(x$freq.merged>15,TRUE,FALSE)
x<-melt(id.vars=c("iri","label","top20"),x)
x$measure<-gsub(".merged","",gsub(".removed","",x$variable))
x$ftype<-gsub("freq.","",gsub("pc.","",x$variable))
x$variable<-NULL
x<-reshape(x, idvar = c("iri","label","ftype","top20"), timevar = "measure", direction = "wide")
names(x)<-gsub("value.","",names(x))
x$freq<-ifelse(is.na(x$freq),0,x$freq)
x$pc<-ifelse(is.na(x$pc),0,x$pc)
x<-x[complete.cases(x), ]
#OUT: x (to be removed after plotting)
```


## Distribution of usage (nr of ontologies) for all PATO classes 

```{r}
ggplot(x,aes(x=reorder(label,freq),y=freq,fill=ftype))+geom_bar(stat="identity",position = "dodge")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  xlab("PATO classes") + ylab("Number of ontologies used in") 
#ggsave("obo_all_mni.png", width = 15, height = 7, units = "cm")
```

## PATO classes used in more than 15 ontologies

```{r}
p<-ggplot(x[x$top20,],aes(x=reorder(label,freq),y=freq,fill=ftype))+geom_bar(stat="identity",position = "dodge")+ geom_text(aes(label=paste("",pc," %",sep="")), hjust=1, color="black",position = position_dodge(width = 1)) +xlab("PATO class") + ylab("Number of ontologies used in") + coord_flip() 
theme_survey(p)
#ggsave("obo_20_plus_mni.png", width = 12, height = 12, units = "cm")
```

## Full breakdown of all PATO classes with use in ontologies (merged imports)
```{r, echo=FALSE}
xl<-x[x$ftype=="merged",]
xl$top20<-NULL
xl$ftype<-NULL
xl<-xl[order(-xl$freq),]
names(xl)<-c("PATO class","Label","Nr. ontologies","% ontologies")
kt(xl)
```

## Full Breadown of usage of PATO classes
in_sig_m:	Number of ontologies where PATO class appears in signature, imports merged

in_sig_ni:	Number of ontologies where PATO class appears in signature, imports removed

tboxabox_merged	Number of ontologies where PATO class appears in TBox or Abox axiom (not RBox), imports merged

tboxabox_noimports	Number of ontologies where PATO class appears in TBox or Abox axiom (not RBox), imports removed

all other:	Number of ontologies using the PATO class as part of a particular axiom type, imports MERGED

The table is large. Note that you can scroll horizontally!

```{r, echo=FALSE}
# P occurs in signature (merged)
d_sig_ct<-count(dsig_m[,c("iri")])
names(d_sig_ct)<-c("iri","in_sig_m")

# P occurs in signature (no imports)
d_sig_ni_ct<-count(dsig_ni[,c("iri")])
names(d_sig_ni_ct)<-c("iri","in_sig_ni")

# P usage TBOX ABOX (imports merged)
ro_cts_m<-unique(dm[,c("iri","o")])
ro_cts_m<-count(ro_cts_m[,c("iri")])
names(ro_cts_m)<-c("iri","tboxabox_merged")

# P usage TBOX ABOX (imports removed)
ro_cts_ni<-unique(dni[,c("iri","o")])
ro_cts_ni<-count(ro_cts_ni[,c("iri")])
names(ro_cts_ni)<-c("iri","tboxabox_noimports")

# P usage broken down by axiom type (imports merged)
ro_ctaxs<-unique(dm[,c("iri","o","axiomtype")])
ro_ctaxs<-count(ro_ctaxs[,c("iri","axiomtype")])
ro_ctaxs<-reshape(ro_ctaxs, idvar = "iri", timevar = "axiomtype", direction = "wide")
names(ro_ctaxs)<-gsub("freq.","",names(ro_ctaxs))

ro_all<-merge(o_labels,ro_cts_m,by="iri",all=TRUE)
ro_all<-merge(ro_all,ro_cts_ni,by="iri",all=TRUE)
ro_all<-merge(ro_all,d_sig_ct,by="iri",all=TRUE)
ro_all<-merge(ro_all,d_sig_ni_ct,by="iri",all=TRUE)
ro_all<-merge(ro_all,ro_ctaxs,by="iri",all=TRUE)
ro_all[is.na(ro_all)] <- 0

ro_all<-ro_all[order(-ro_all$tboxabox_merged),]
kt(ro_all)
#write.csv(ro_all,file="ro.csv")

```

```{r cleanobo, echo=FALSE}
#x<-dm<-dni<-dm<-dni<-corpus<-dsig_m<-dsig_ni<-ct_unique_o_using_rel<-ct_unique_rel_tbox_abox<-ct_unique_o_using_rel_ni<-ct_unique_rel_tbox_abox_ni<-NULL
```


```{r prepromain, echo=FALSE}
# IN: df_ax
ct_axt<-count(df_ax[,.(ftype,corpus,iri,axiomtype,label)])
ct_axt<-ct_axt[order(-ct_axt$freq),]

df_axo<-unique(df_ax[,.(o,ftype,corpus,axiomtype,iri)])
ct_axto<-count(df_axo[,.(ftype,corpus,iri,axiomtype)])
ct_axto<-merge(ct_axto,df_pato,by.x = "iri",by.y = "term",all.x = TRUE)
ct_axto<-ct_axto[order(-ct_axto$freq),]

ct_p<-count(df_p[,.(ftype,corpus,iri,label,corpussize)])
ct_p$pc<-pc(ct_p$freq,ct_p$corpussize)
#ct_p<-merge(ct_p,df_ro,by.x = "iri",by.y = "entity",all = TRUE) //every relation is used at least once, else this would be necessary.
ct_p<-ct_p[order(-ct_p$freq),]

ct_o<-count(df_p[,.(ftype,corpus,o)])
ct_o<-ct_o[order(-ct_o$freq),]

df_po<-unique(df_p[,.(ftype,corpus,corpussize,o)])
ct_ro<-count(df_po[,.(ftype,corpus,corpussize)])
ct_ro$pc<-pc(ct_ro$freq,ct_ro$corpussize)

ct_ax<-count(df_ax[,.(ftype,corpus,iri,label)])
names(ct_ax)<-c("ftype","corpus","iri","label","axioms")

ct_p<-merge(ct_p,ct_ax,by=c("ftype","corpus","iri","label"),all = TRUE)

```

# Other metrics (just dumped here)

## How many ontologies use PATO?

This usage is based on whether an ontology contained a  PATO class in its signature. This includes any axiom types (such as property characteristics), including declarations!
```{r, echo=FALSE}
x<- ct_ro
names(x)<-c("Imports","Corpus","Corpus size","Ontologies using PATO","% Ontologies using PATO")
kt(x)
```


## How many different PATO classes does this ontology use?

Compared to the previous plot (very similar), this plot takes into account all axiom types, not just TBOX and ABOX!

```{r, echo=FALSE}
dgg<-df_ax
dgg<-merge(dgg,unique(df_p[,c("ftype","corpus")]),by=c("ftype","corpus"),all.x = TRUE)
dgg<-unique(dgg[,c("label","o","corpussize")])
cdgg<-count(dgg[,c("label","corpussize")])
cdgg$pc<-pc(cdgg$freq,cdgg$corpussize)
#cdgg<-cdgg[cdgg$freq>=input$rel_ct_offset[1]&cdgg$freq<=input$rel_ct_offset[2],]
ggplot(cdgg[cdgg$freq>15,],aes(x=reorder(label,freq),y=freq))+geom_bar(stat="identity")+ geom_text(aes(label=paste(freq," (",pc," %)",sep="")), hjust=1.1, color="white") +xlab("PATO class") + ylab("Number of ontologies used in") + coord_flip() + ggtitle("Top relations (used by more than 20 ontologies)")


asis_output("### The following table shows the number of distinct PATO classes used across the selected axiom types")

asis_output("For example, the HP ontology might be using 45")

dgg<-unique(df_ax[,c("label","o")])
cdgg<-count(dgg[,c("o")])
#cdgg<-cdgg[cdgg$freq>=input$rel_ct_offset[1]&cdgg$freq<=input$rel_ct_offset[2],]
cdgg<-cdgg[order(-cdgg$freq),]
names(cdgg)<-c("Ontology","Number of PATO classes used")
kt(cdgg)

```


```{r, echo=FALSE, include=FALSE}
## What kind of axiomtype is the PATO classes used in? In how many axioms of that type is it used?
#IN: ct_axt (needs to be reactive!)
x<- ct_axt[,c("iri","label","axiomtype","freq")]
names(x)<-c("PATO classes","Label","Axiomtype","Number of axioms")
kt(x)
```

```{r, echo=FALSE, include=FALSE}
## What kind of axiomtype is the PATO class used in? In how many ontologies?
x<-ct_axto[,c("iri","axiomtype","freq")]
names(x)<-c("PATO class","Axiomtype","Nr. of ontologies")
kt(x)

```

```{r, echo=FALSE}
asis_output("What kind of class expressions are PATO classes used in? In how many axioms of that type is it used?")
x<-unique(df_exp[,.(ftype,corpus,iri,expressiontype,axiomid,o)])
x<-count(x[,.(ftype,corpus,iri,expressiontype)])

x<-x[,c("iri","expressiontype","freq")]
x<-merge(x,o_labels,by=c("iri"),all.x=TRUE)
x<-x[order(-x$freq),]
names(x)<-c("PATO class","Expression type","Nr. axioms","Label")
kt(x[,c("PATO class","Label","Expression type","Nr. axioms")])

asis_output("What kind of class expressions is the PATO classes used in? In how many ontologies?")
x<-df_expo[,]
x<-count(x[,.(ftype,corpus,iri,expressiontype)])
x<-x[,c("iri","expressiontype","freq")]
x<-merge(x,o_labels,by=c("iri"),all.x=TRUE)
x<-x[order(-x$freq),]
names(x)<-c("PATO class","Expression type","Nr. ontologies","Label")
#kt(x[,c("PATO class","Label","Expression type","Nr. ontologies")])

```


```{r, echo=FALSE, include=FALSE}
# Full breakdown of  PATO classes used across ontologies
# A class is 'used' by the ontology if it appears in its signature.
x<-unique(df_ax[,c("iri","label","o","axiomid")])
x<-count(x[,c("iri","label","o")])
names(x)<-c("PATO class", "Label","Ontology","Number of axioms")
#kt(x)
```

```{r}
turtle<-function(df,name,dt) {
  #  "suahdius" .
  names(df)<-c("iri","val")
  write.csv(df,paste(name,".csv",sep=""),row.names = FALSE)
  fileConn<-file(paste(name,".ttl",sep=""))
  writeLines(paste("<",df$iri,"> <http://www.purl.obolibrary.org/obo/DEV_",name,"> \"",df$val,"\"^^",dt, ". ",sep=""), fileConn)
  close(fileConn)
}
```

```{r}
ttl_ax<-unique(da[corpus=="obo20190313"&ftype=="merged",c("iri","o","axiomid")])
ttl_ax$id<-paste(ttl_ax$o,ttl_ax$axiomid,sep = "-")
ttl_ax_id = ttl_ax[,c("id","iri")]
ct_ttl_iri<-count(ttl_ax_id[,c("iri")])

ttl_ax_o<-unique(da[corpus=="obo20190313"&ftype=="merged",c("iri","o")])
ct_ttl_ax_o<-count(ttl_ax_o[,c("iri")])

ttl_exp<-unique(df_exp[corpus=="obo20190313"&ftype=="merged",.(iri,expressionid,axiomid,o)])
ttl_exp$axid<-paste(ttl_exp$o,ttl_exp$axiomid,sep = "-")
ttl_exp<-ttl_exp[axid %in% unique(ttl_ax$id),]
ttl_exp$id<-paste(ttl_exp$o,ttl_exp$axiomid,ttl_exp$expressionid,sep = "-")
ttl_exp = ttl_exp[,c("id","iri")]
ct_ttl_exp<-count(ttl_exp[,c("iri")])

cumulative_branch<-unique(df_p[corpus=="obo20190313"&ftype=="merged"&!is.na(impact),.(iri,o,impact)])
sum_cumulative_branch<-aggregate(cumulative_branch$impact,by=list(cumulative_branch$iri),FUN=sum)

turtle(sum_cumulative_branch,"ct_branch_impact","xsd:int")
turtle(ct_ttl_iri,"ct_uses_across_axioms","xsd:int")
turtle(ct_ttl_ax_o,"ct_uses_across_ontologies","xsd:int")
turtle(ct_ttl_exp,"ct_uses_across_expressions","xsd:int")
turtle(ttl_ax_o,"used_in_ontology","xsd:string")
```

# Additional information
```{r, echo=FALSE}
asis_output("https://monarchinitiative.org/")
```
